---
title: "Sketches"
description: |
  Project rationale, goals, and target scenarios.
author:
  - name: Taren Sanders 
    url: https://github.com/tarensanders
    affiliation: IPPE, Australian Catholic University
    affiliation_url: https://www.acu.edu.au/research-and-enterprise/our-research-institutes/institute-for-positive-psychology-and-education
    orcid_id: 0000-0002-4504-6008
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-data}
library(screenviz)
library(tidyverse)

df <- screenviz::load_data()
```

# Scenarios

There are two groups of users we think might want to access the system. Example use cases are given below.

## Scenario One

**Users:** Parents

> A parent wants to explore the types of exposure.
> The select a particular exposure (e.g., TV) might impact their child.
> They search for the exposure and are given an overview of the known outcome categories.
> Visualise info about the uncertainty for each effect.
> They filter the results for their child's age.
> They click into an outcome category to get more information on the result (e.g., text summary, info about reason for the uncertainty).

# Scenario Two

**Users:** Researchers/clinicians

> A domain expert wants to explore evidence for screen time in more detail.
> Use the system to get an overview of the evidence (exposure, outcome, effect size).
> They search for the exposure and/or the outcome, and optionally filter by age.
> They click into a relationship and can access the forest plot of the original studies, and the link to the original meta-analysis (and other, related studies, uncertainty). Three levels: evidence, uncertainty, meta-data.

# Tasks/Screens

## Task One

> Explore the exposures that there are evidence for.

**Proposed Idiom:** Heatmap

### Counts

```{r hm-counts}
df %>%
  group_by(general_exposure, general_outcome) %>%
  summarise(n = n()) %>%
  ggplot(aes(x = general_exposure, y = general_outcome, fill = n)) +
  geom_tile() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

### Effect sizes

```{r hm-es}
df %>%
  group_by(general_exposure, general_outcome) %>%
  summarise(r = mean(r)) %>%
  ggplot(aes(x = general_exposure, y = general_outcome, fill = r)) +
  geom_tile() +
  scale_fill_distiller(palette = "RdBu", limits = c(-.5, .5)) +
  theme_minimal()
```

### Notes

* Could show these side-by-side
* Could further reduce the number of categories (e.g., to just "Health", "Education", etc)
* At the moment the effect size is just taking the mean, but I think it would be more sensible to rerun the meta-analysis
* The proposed interaction (to move to more detailed screen) would be to click one of:
  - Exposure(y - axis label)
  - Outcome(x - axis label)
  - Effect size (cell of heatmap)

## Task Two

> Explore an overview of the outcome categories for the selected exposure category.

(*E.g., if they have chosen 'video games'*)

### Option One (Heatmap)

```{r}
df %>%
  filter(general_exposure == "Video games") %>%
  group_by(plain_language_exposure, plain_language_outcome) %>%
  summarise(r = mean(r)) %>%
  ggplot(aes(
    x = plain_language_exposure,
    y = plain_language_outcome, fill = r
  )) +
  geom_tile() +
  scale_fill_distiller(palette = "RdBu", limits = c(-.5, .5)) +
  theme_minimal()
```

### Option  Two (Line Range)

```{r}
p_df <- df %>%
  filter(general_exposure == "Video games") %>%
  select(
    general_exposure, general_outcome, plain_language_exposure,
    plain_language_outcome, r, r_ub, r_lb, age_group, n
  ) %>%
  mutate(plain_language_outcome = fct_reorder(plain_language_outcome, r)) %>%
  arrange(plain_language_outcome, r) %>%
  group_by(general_exposure, plain_language_outcome) %>%
  mutate(
    effect_id = row_number(),
    group_id = cur_group_id(),
    median_effect = median(r)
  ) %>%
  ungroup() %>%
  arrange(desc(median_effect), plain_language_outcome, desc(r)) %>%
  mutate(
    aux = row_number()
  ) %>%
  group_by(plain_language_outcome) %>%
  mutate(breaks = median(aux)) %>%
  ungroup() %>%
  mutate(
    stripe = factor(if_else(group_id %% 2 == 0, 1, 0))
  )

ggplot(p_df, aes(
  x = aux,
  y = r
)) +
  geom_linerange(aes(
    ymin = r_lb,
    ymax = r_ub,
    col = age_group
  ), size = 3) +
  geom_point(aes(
    size = log(n)
  ),
  shape = 21,
  color = "white", stroke = 0.5, fill = "black"
  ) +
  geom_rect(
    aes(
      xmax = aux + 0.5, xmin = aux - 0.5,
      ymin = -1, ymax = 1, fill = stripe
    ),
    alpha = 0.4
  ) +
  scale_y_continuous(name = "Correlation", limits = c(-1, 1)) +
  scale_x_continuous("Outcome",
    labels = unique(p_df$plain_language_outcome),
    breaks = unique(p_df$breaks)
  ) +
  scale_fill_manual(values = c("white", "grey50"), guide = "none") +
  scale_size(guide = "none") +
  coord_flip() +
  theme_minimal()
```

### Notes

* I think the heatmap is likely to be more intuitive 
* We could instead put the line range in the tooltip or in the next screen
* The proposed interaction would be hover and click in for details
* Study quality could also be in the tooltip


## Task Three

> Show detailed information about the effect

*TODO* - I think this will likely be a formatted page with an interpretation, plus original forest plot and links to studies for 'expert' users.