---
title: "Deployment"
description: |
  Documents the steps for deploying the app (work-in-progress).
site: distill::distill_website
---

```{r setup, include=FALSE}
```

# Updating and deploying the app

## Running locally

This project is setup as an R package, which means you can set it up to run in the same way you would any other R package that isn't on CRAN.
Run `devtools::install_github("tarensanders/screen_viz")` to install the package locally.

Before you can run it, you will need to make sure that app can access data from Cloudstor.
To do this, you need two things:

1. Access to the folder `Shared/screenviz` on Cloudstor (ask Taren for access if you don't have it).
1. A set of environment variables to provide the app with API access to the folder.
These should be called `CLOUD_USER` and `CLOUD_PASS`.
See the [Cloudstor documentation](https://support.aarnet.edu.au/hc/en-us/articles/236034707-How-do-I-manage-change-my-passwords-) for how to create and app password.
The easiest way to edit your R environment is to use `usethis::edit_r_environ()`, then restart the session.
1. You can then run the app with `screenviz::screenviz_app()`.

## Making changes

To make edits to the app, you need a slightly different workflow.
Note that you still need the requirements (folder access and environment variables) to run the app.

1. Clone the [GitHub Repo](https://github.com/tarensanders/screen_viz) using whatever workflow you like.
1. Install the project dependencies using `devtools::install_deps()` and (optionally) `devtools::install_dev_deps()`.
1. To check everything is setup, you can run `devtools::check()` or `devtools::install()`.
1. You can then run the app with `devtools::load_all(); devtools::screenviz_app()`, or by sourcing `app.R`.

To make changes, you need to commit changes to a new branch and open a PR to merge to either `main` or `dev`.
You cannot make changes directly to `main`.
Before opening a PR, make sure to run `devtools::check()` and `devtools::install()` to check for build errors.
If your change adds new functions, please try to include a test and ensure it runs with `devtools::test()`.

PRs to `main` or `dev` will run `R-CMD-CHECK` using GitHub actions, and when the pull request is merged it will automatically be deployed to either the live app or the dev version.

# Updating this website

## Update non-article pages

To update the non-article components of the site, run the following commands from the project root:

```{r, eval = FALSE}
rmarkdown::render_site("docs")
```
Note that this **won't** rerun any of the files in `docs/_articles`. 
Those need to be rerendered before the site is updated.
The changes can then be pushed to GitHub to update the pages.
Note that the changes are only visible if made in the `main` branch.

## Update/create an article page

The steps for creating or updating an article are:

1. Create a new article in `docs/_articles` with `output: distill::distill_article` as the output.
1. Once written, knit the article using whatever method you like (knit button, call to `rmarkdown`, etc).

The steps for a new non-article page are:

1. Create an Rmd file in the `docs` folder with `site: distill::distill_website` as the output. 
1. There's no need to render these, as it's done when the site is updated.

Regardless of if it is an article or just a page, the following steps are required:

1. Make sure that the page is accessible somehow.
Most likely that means updating `_site.yml` to include a link in the navbar.
1. Render the site using `rmarkdown::render_site("docs")` from the project root.
1. Push changes to GitHub.
Once merged into `main`, the GitHub pages will update automatically.
